Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-10 introduction.tex
lloid_paper: citep -> citet where appropriate
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1013 ccdd05d5-56c1-461a-bf98-85f6876523b4

The coalescence of compact binary systems consisting of neutron stars
 (\textsc{ns}) and/or black holes (\textsc{bh}) is presently the best
understood and most actively pursued target source of gravitational
radiation for ground-based gravitational-wave (\GW{}) detectors.
As a compact binary system loses energy to \GW{}s, its
orbital separation decays, leading to a run-away inspiral with the \GW{}
amplitude and frequency increasing until the system eventually merges.  It is
thought that if a \textsc{ns} is involved, it may become tidally disrupted near
the merger and fuel a bright electromagnetic (\EM{})
counterpart~\citep{shibata:2007}. Observation of an \EM{} counterpart to a
candidate \GW{} event will vastly boost confidence in the \GW{} detection and
will often provide sufficient sky localization to determine
the source's host galaxy and therefore measure the source's redshift. The
\GW{} observation of this event will also provide a luminosity
distance measurement. With both quantities, we can
immediately measure the Hubble constant with unprecedented
accuracy~\citep{2010ApJ...725..496N}. The most efficient means of obtaining
such joint observations is through the rapid identification and dissemination
of candidate \GW{} events.

@@

We show that by examining the signal to noise ratio (\SNR{}) stream for
threshold crossings before the \GW{} signal leaves the detection band, it is
possible to trade some \SNR{} and sky localization
accuracy for negative latency.  Figure~\ref{fig:earlywarning} shows
projected early trigger rates for \textsc{ns}--\textsc{ns} binaries in Advanced
\LIGO\ assuming event rates predicted in~\citep{Abadie:2010p10836} and anticipated
detector sensitivity described in \citep{ALIGONoise}.  The
most likely estimates indicate that $\sim$10 sources will produce an \SNR\
above 8 in the detector 10 seconds or more prior to the merger during one
year of observation, though the uncertainty spans orders of magnitude.
The gray bands give the 5 to 95\% confidence interval as described
in~\citep{Abadie:2010p10836}.
%
\begin{figure}[h]
\plotone{figures/snr_in_time.pdf}
\caption{\label{fig:earlywarning} Expected number of \textsc{ns}--\textsc{ns}
sources that will be detectable $t$ seconds before coalescence.  The heavy
solid line is the most likely yearly rate estimate $\dot N_{\mathrm{re}}$
during Advanced \LIGO.  The shaded region represents the confidence interval
$[\dot N_{\mathrm{low}}, \dot N_{\mathrm{high}}]$ described in
\citep{Abadie:2010p10836}.  With an advanced detector in the `zero detuning,
high power' configuration \citep{ALIGONoise} and an \SNR\ threshold of 8,
we will observe a total of $\dot N_{\mathrm{re}} = 40$ events~yr$^{-1}$, but
$\sim$10~yr$^{-1}$ will be detectable within 10~s of merger and
$\sim$1~yr$^{-1}$ within 100~s.}
\end{figure}

@@

Realizing advance detection of compact binary coalescences (\CBC{}s) will
require striking a balance between latency and throughput. \CBC{} searches
consist of banks of matched filters, or
cross-correlations between the data stream and a bank of nominal ``template''
signals.  There are many different implementations of matched filters, but most
have high throughput at the cost of high latency, or low latency at the cost of
low throughput.  The former are epitomized by the overlap-save algorithm
\citep{numerical-recipes-chapter-13} for frequency domain (\FD) convolution,
currently the preferred method in \GW{}
searches.  The most obvious example of the latter is the time domain
(\TD) convolution, which has no algorithmic latency.  However, its
computational complexity is quadratic in the length of the templates, so it is
prohibitively expensive for long templates.

>>>>

The coalescence of compact binary systems consisting of neutron stars
 (\textsc{ns}) and/or black holes (\textsc{bh}) is presently the best
understood and most actively pursued target source of gravitational
radiation for ground-based gravitational-wave (\GW{}) detectors.
As a compact binary system loses energy to \GW{}s, its
orbital separation decays, leading to a run-away inspiral with the \GW{}
amplitude and frequency increasing until the system eventually merges.  It is
thought that if a \textsc{ns} is involved, it may become tidally disrupted near
the merger and fuel a bright electromagnetic (\EM{})
counterpart~\citep{shibata:2007}. Observation of an \EM{} counterpart to a
candidate \GW{} event will vastly boost confidence in the \GW{} detection and
will often provide sufficient sky localization to determine
the source's host galaxy and therefore measure the source's redshift. The
\GW{} observation of this event will also provide a luminosity
distance measurement. With both quantities, we can
immediately measure the Hubble constant with unprecedented
accuracy and systematics independent of the standard cosmic distance
ladder~\citep{2010ApJ...725..496N}. The most efficient means of obtaining
such joint observations is through the rapid identification and dissemination
of candidate \GW{} events.

@@

We show that by examining the signal to noise ratio (\SNR{}) stream for
threshold crossings before the \GW{} signal leaves the detection band, it is
possible to trade some \SNR{} and sky localization
accuracy for negative latency.  Figure~\ref{fig:earlywarning} shows
projected early trigger rates for \textsc{ns}--\textsc{ns} binaries in Advanced
\LIGO\ assuming event rates predicted in \citet{Abadie:2010p10836} and anticipated
detector sensitivity described in \citet{ALIGONoise}.  The
most likely estimates indicate that $\sim$10 sources will produce an \SNR\
above 8 in the detector 10 seconds or more prior to the merger during one
year of observation, though the uncertainty spans orders of magnitude.
The gray bands give the 5 to 95\% confidence interval as described
in \citet{Abadie:2010p10836}.
%
\begin{figure}[h]
\plotone{figures/snr_in_time.pdf}
\caption{\label{fig:earlywarning} Expected number of \textsc{ns}--\textsc{ns}
sources that will be detectable $t$ seconds before coalescence.  The heavy
solid line is the most likely yearly rate estimate $\dot N_{\mathrm{re}}$
during Advanced \LIGO.  The shaded region represents the confidence interval
$[\dot N_{\mathrm{low}}, \dot N_{\mathrm{high}}]$ described in
\citep{Abadie:2010p10836}.  With an advanced detector in the `zero detuning,
high power' configuration \citep{ALIGONoise} and an \SNR\ threshold of 8,
we will observe a total of $\dot N_{\mathrm{re}} = 40$ events~yr$^{-1}$, but
$\sim$10~yr$^{-1}$ will be detectable within 10~s of merger and
$\sim$1~yr$^{-1}$ within 100~s.}
\end{figure}

@@

Realizing advance detection of compact binary coalescences (\CBC{}s) will
require striking a balance between latency and throughput. \CBC{} searches
consist of banks of matched filters, or
cross-correlations between the data stream and a bank of nominal ``template''
signals.  There are many different implementations of matched filters, but most
have high throughput at the cost of high latency, or low latency at the cost of
low throughput.  The former are epitomized by the overlap-save algorithm~%
\citep{numerical-recipes-chapter-13} for frequency domain (\FD) convolution,
currently the preferred method in \GW{}
searches.  The most obvious example of the latter is the time domain
(\TD) convolution, which has no algorithmic latency.  However, its
computational complexity is quadratic in the length of the templates, so it is
prohibitively expensive for long templates.

### 2011-06-10 method.tex
lloid_paper: citep -> citet where appropriate
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1013 ccdd05d5-56c1-461a-bf98-85f6876523b4

In this section we describe a decomposition of the \CBC{} waveform space that
reduces time-domain (\TD) filtering cost sufficiently to allow for the
possibility of \earlywarning\ detection with modest computing requirements.  We
expand on the ideas of~\citep{Marion2004, Buskulic2010} that describe a
multi-band decomposition of the compact binary parameter space that resulted in
a search with minutes latency in \LIGO{}'s S6 and Virgo's VSR3 joint science
runs~\citep{HugheyGWPAW2011}.  We combine this with the \SVD\ rank-reduction
method of~\citep{Cannon:2010p10398} that exploits the redundancy of
the template banks.

@@

The first step of our proposed method is to divide the templates into time
slices in a \TD{} analogue to the \FD{} decomposition described
in~\citep{Marion2004, Buskulic2010}.  To wit, we decompose each template
$h_{i}[k]$ into a sum of $S$ non-overlapping filters
%
\begin{equation}
\label{eq:time-slices}
h_{i}[k] = \sum_{s=0}^{S-1}
	\begin{cases}
		h_i^s[k] & \textrm{if } t^s \leqslant k / f^0 < t^{s+1} \\
		0 & \textrm{otherwise}
	\end{cases}
\end{equation}
%
for $S$ integers $\{f^0 t^s\}$ such that $0  = f^0 t^0 < f^0 t^1 < \cdots < f^0
t^S = N$.  A matched filter is constructed for each time slice.  The outputs
form an ensemble of partial \SNR{} streams.  By linearity of the filtering
process, these partial \SNR\ streams can be suitably time-delayed and summed to
 reproduce the \SNR\ of the full template.

@@

As described previously, the template banks are, by design, highly correlated.
It is possible to greatly reduce the number of filters required to achieve a
particular minimum match by designing an appropriate set of \SVD\ {\em
basis templates}, previously demonstrated
in~\citep{Cannon:2010p10398}.  Similarly, the time-sliced templates described
above can be approximated to arbitrary accuracy by expansion into a set of
\SVD\ \emph{basis templates}, $u_l^s[k]$, related to the original time
sliced templates through the \emph{reconstruction matrix},
$v_{il}^s\sigma_l^s$:
%
\begin{equation}
h_i^s[k] = \sum_{\mathclap{l=0}}^{\mathclap{M-1}} v_{il}^s \sigma_l^s u_l^s[k] \approx \sum_{\mathclap{l=0}}^{\mathclap{L^s-1}} v_{il}^s \sigma_l^s u_l^s[k].
\label{eq:svddecomp}
\end{equation}
%
The parameter $\numsvdtmps$ is the number of basis templates that are kept in
the approximation.  This determines the \SVD\ tolerance, which affects the
\SNR\ loss due to the approximation.  The authors of \citep{Cannon:2010p10398}
showed that high accuracy could be achieved with far fewer basis templates than
templates in the original template bank.  We find that when combined with the
time-slice decomposition, the number of basis templates \numsvdtmps\ is much
smaller than the original number of templates \numtmps\ and improves on
\citep{Cannon:2010p10398} by nearly an order of magnitude.  In the next section
we describe how we form our early-warning detection statistic using the time-slice
decomposition and the \SVD.

@@

The most common \FD{} method is known as the \emph{overlap-save} algorithm, described in \citep{numerical-recipes-chapter-13}.  It entails splitting the input into blocks of $D$ samples, $D > \tmpsamps$, each block overlapping the previous one by $D - \tmpsamps$ samples.  For each block, the algorithm computes the forward \fft\ of the data and the templates, multiplies them, and then computes the reverse \fft.

>>>>

In this section we describe a decomposition of the \CBC{} waveform space that
reduces time-domain (\TD) filtering cost sufficiently to allow for the
possibility of \earlywarning\ detection with modest computing requirements.  We
expand on the ideas of \citet{Marion2004, Buskulic2010} that describe a
multi-band decomposition of the compact binary parameter space that resulted in
a search with minutes latency in \LIGO{}'s S6 and Virgo's VSR3 joint science
runs~\citep{HugheyGWPAW2011}.  We combine this with the \SVD\ rank-reduction
method of \citet{Cannon:2010p10398} that exploits the redundancy of
the template banks.

@@

The first step of our proposed method is to divide the templates into time
slices in a \TD{} analogue to the \FD{} decomposition described
in \citet{Marion2004, Buskulic2010}.  To wit, we decompose each template
$h_{i}[k]$ into a sum of $S$ non-overlapping filters
%
\begin{equation}
\label{eq:time-slices}
h_{i}[k] = \sum_{s=0}^{S-1}
	\begin{cases}
		h_i^s[k] & \textrm{if } t^s \leqslant k / f^0 < t^{s+1} \\
		0 & \textrm{otherwise}
	\end{cases}
\end{equation}
%
for $S$ integers $\{f^0 t^s\}$ such that $0  = f^0 t^0 < f^0 t^1 < \cdots < f^0
t^S = N$.  A matched filter is constructed for each time slice.  The outputs
form an ensemble of partial \SNR{} streams.  By linearity of the filtering
process, these partial \SNR\ streams can be suitably time-delayed and summed to
 reproduce the \SNR\ of the full template.

@@

As described previously, the template banks are, by design, highly correlated.
It is possible to greatly reduce the number of filters required to achieve a
particular minimum match by designing an appropriate set of \SVD\ {\em
basis templates}, previously demonstrated
in \citet{Cannon:2010p10398}.  Similarly, the time-sliced templates described
above can be approximated to arbitrary accuracy by expansion into a set of
\SVD\ \emph{basis templates}, $u_l^s[k]$, related to the original time
sliced templates through the \emph{reconstruction matrix},
$v_{il}^s\sigma_l^s$:
%
\begin{equation}
h_i^s[k] = \sum_{\mathclap{l=0}}^{\mathclap{M-1}} v_{il}^s \sigma_l^s u_l^s[k] \approx \sum_{\mathclap{l=0}}^{\mathclap{L^s-1}} v_{il}^s \sigma_l^s u_l^s[k].
\label{eq:svddecomp}
\end{equation}
%
The parameter $\numsvdtmps$ is the number of basis templates that are kept in
the approximation.  This determines the \SVD\ tolerance, which affects the
\SNR\ loss due to the approximation.  The authors of \citet{Cannon:2010p10398}
showed that high accuracy could be achieved with far fewer basis templates than
templates in the original template bank.  We find that when combined with the
time-slice decomposition, the number of basis templates \numsvdtmps\ is much
smaller than the original number of templates \numtmps\ and improves on
\citep{Cannon:2010p10398} by nearly an order of magnitude.  In the next section
we describe how we form our early-warning detection statistic using the time-slice
decomposition and the \SVD.

@@

The most common \FD{} method is known as the \emph{overlap-save} algorithm, described in \citet{numerical-recipes-chapter-13}.  It entails splitting the input into blocks of $D$ samples, $D > \tmpsamps$, each block overlapping the previous one by $D - \tmpsamps$ samples.  For each block, the algorithm computes the forward \fft\ of the data and the templates, multiplies them, and then computes the reverse \fft.

### 2011-06-10 results.tex
Table now spans two columns
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1002 ccdd05d5-56c1-461a-bf98-85f6876523b4
Tweaks to figure 4
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1005 ccdd05d5-56c1-461a-bf98-85f6876523b4
lloid_paper: citep -> citet where appropriate
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1013 ccdd05d5-56c1-461a-bf98-85f6876523b4

We examine the performance of the \lloid\ algorithm on a small region of
compact binary parameter space centered on typical \textsc{ns}--\textsc{ns}
masses.  We begin by constructing a template bank that spans component masses
between 1~and~3~$M_\odot$ using a simulated Advanced \LIGO{} noise
curve~\citep{ALIGONoise}.  Then we create sub-banks by partitioning the parameter
space by chirp mass.  Figure \ref{fig:tmpltbank} illustrates this procedure.
\begin{figure}[h]
	\plotone{figures/tmpltbank.png}
	\caption{\label{fig:tmpltbank}Placement of template parameters used in this paper.  The template bank consists of 98544 templates with component masses $m_1$, $m_2$, between 1~and~3~$M_\odot$.  We design a filter bank to search for a subset of 657 of these templates with chirp masses $\mathcal M$ between 1.1955~and~1.2045~$M_\odot$.}
\end{figure}
The result is that we obtain 657 templates with chirp masses between 1.1955~and~1.2045~$M_\odot$.  With this
sub-bank we were able to construct an efficient time-slice decomposition that consisted of 11 time slices
with sample rates between 32 and 4096 Hz shown in table \ref{tab:time_slices}.
\begin{table}
\caption{\label{tab:time_slices} Filter design for these 657 templates.  From left to right, this table shows the sample rate, time interval, number of samples, and number of orthogonal templates for each time slice.  We vary \SVD{} tolerance from $\left(1-10^{-1}\right)$ to $\left(1-10^{-6}\right)$.}
\begin{tabular}{rr@{,\,}lc*{6}{r}}
\tableline\tableline
\multicolumn{4}{c}{} &\multicolumn{6}{c}{$\log_{10}$ (1$-$\SVD{} tolerance)} \\
%\multicolumn{4}{c}{} &\tableline \\
$f^s$ (Hz) & $[t^s$&$t^{s+1})$ (s) & $N^s$ & $-1$ & $-2$ & $-3$ & $-4$ & $-5$ & $-6$ \\
\tableline
4096 & [0&0.5) & 2048 & 1 & 4 & 6 & 8 & 10 & 14 \\
512 & [0.5&4.5) & 2048 & 2 & 6 & 8 & 10 & 12 & 16 \\
256 & [4.5&12.5) & 2048 & 2 & 6 & 8 & 10 & 12 & 15 \\
128 & [12.5&76.5) & 8192 & 6 & 20 & 25 & 28 & 30 & 32 \\
64 & [76.5&140.5) & 4096 & 1 & 8 & 15 & 18 & 20 & 22 \\
64 & [140.5&268.5) & 8192 & 1 & 7 & 21 & 25 & 28 & 30 \\
64 & [268.5&396.5) & 8192 & 1 & 1 & 15 & 20 & 23 & 25 \\
32 & [396.5&460.5) & 2048 & 1 & 1 & 3 & 9 & 12 & 14 \\
32 & [460.5&588.5) & 4096 & 1 & 1 & 7 & 16 & 18 & 21 \\
32 & [588.5&844.5) & 8192 & 1 & 1 & 8 & 26 & 30 & 33 \\
32 & [844.5&1100.5) & 8192 & 1 & 1 & 1 & 12 & 20 & 23 \\
\tableline
\end{tabular}
\end{table}
We use this template bank and decomposition for the remainder of this section.

@@

In this section we check the effect of the \SVD\ tolerance parameter defined
in~\citep{Cannon:2010p10398}.  By changing the tolerance of the reconstruction
of the physical waveforms one directly affects the mismatch that results from
the truncation of the orthogonal filter matrix.  The conditions presented here
are more complicated than in the original work~\citep{Cannon:2010p10398} due to
the inclusion of the time-sliced templates and re-sampling.  Figure~%
\ref{fig:hist-svd-tolerance} demonstrates that it is possible to achieve
typical \SNR\ losses of $\ll1\%$.  However, we do notice that the mismatch
saturates with respect to the tolerance.  This could be the effect of the
re-sampling, or another \SNR\ loss that we did not model or expect.  However the
saturation is still an order of magnitude below our target mismatch of
$\sim$0.003.  We find that an \SVD\ tolerance of $\left(1-10^{-4}\right)$ is
adequate to achieve our target \SNR{} loss.
%
\begin{figure}
		\subfloat[Mismatch versus \textsc{svd} tolerance]{\label{fig:hist-svd-tolerance}\includegraphics{figures/bw.pdf}}
		\subfloat[Mismatch versus $N^\shortuparrow$]{\label{fig:hist-interpolate}\includegraphics{figures/bw_resample.pdf}}
		\caption{Box-and-whisker plot of mismatch between nominal
template bank and \lloid\ measured impulse responses.  The upper and lower boundaries of
the boxes show the upper and lower quartiles; the lines in the center denote the medians.
The whiskers represent the minimum and maximum mismatch over all templates.  In 
\subref{fig:hist-svd-tolerance} the interpolation filter length is held fixed
at $N^\shortuparrow = 192$, while the \SVD\ tolerance is varied from
$\left(1-10^{-1}\right)$ to $\left(1-10^{-6}\right)$.  In \subref{fig:hist-interpolate}, the \SVD\ tolerance is fixed at $\left(1-10^{-6}\right)$ while $N^\shortuparrow$ is varied from 8 to 192 coefficients.}
\end{figure}

@@

>>>>

We examine the performance of the \lloid\ algorithm on a small region of
compact binary parameter space centered on typical \textsc{ns}--\textsc{ns}
masses.  We begin by constructing a template bank that spans component masses
between 1~and~3~$M_\odot$ using a simulated Advanced \LIGO{} noise
curve~\citep{ALIGONoise}.  Then we create sub-banks by partitioning the parameter
space by chirp mass.  Figure \ref{fig:tmpltbank} illustrates this procedure.
\begin{figure}[h]
	\plotone{figures/tmpltbank.png}
	\caption{\label{fig:tmpltbank}Placement of template parameters used in this paper.  The template bank consists of 98544 templates with component masses $m_1$, $m_2$, between 1~and~3~$M_\odot$.  We design a filter bank to search for a subset of 657 of these templates with chirp masses $\mathcal M$ between 1.1955~and~1.2045~$M_\odot$.}
\end{figure}
The result is that we obtain 657 templates with chirp masses between 1.1955~and~1.2045~$M_\odot$.  With this
sub-bank we were able to construct an efficient time-slice decomposition that consisted of 11 time slices
with sample rates between 32 and 4096 Hz shown in table \ref{tab:time_slices}.
\begin{table*}
\begin{center}
\caption{\label{tab:time_slices} Filter design for these 657 templates.  From left to right, this table shows the sample rate, time interval, number of samples, and number of orthogonal templates for each time slice.  We vary \SVD{} tolerance from $\left(1-10^{-1}\right)$ to $\left(1-10^{-6}\right)$.}
\begin{tabular}{rr@{,\,}lc*{6}{r}}
\tableline\tableline
\\ [-1.5ex]
\multicolumn{4}{c}{} &\multicolumn{6}{c}{$\log_{10}$ (1$-$\SVD{} tolerance)} \\ [1ex]
\cline{5-10}
\\ [-1.5ex]
$f^s$ (Hz) & $[t^s$&$t^{s+1})$ (s) & $N^s$ & $-1$ & $-2$ & $-3$ & $-4$ & $-5$ & $-6$ \\ \tableline
4096 & [0&0.5) & 2048 & 1 & 4 & 6 & 8 & 10 & 14 \\
512 & [0.5&4.5) & 2048 & 2 & 6 & 8 & 10 & 12 & 16 \\
256 & [4.5&12.5) & 2048 & 2 & 6 & 8 & 10 & 12 & 15 \\
128 & [12.5&76.5) & 8192 & 6 & 20 & 25 & 28 & 30 & 32 \\
64 & [76.5&140.5) & 4096 & 1 & 8 & 15 & 18 & 20 & 22 \\
64 & [140.5&268.5) & 8192 & 1 & 7 & 21 & 25 & 28 & 30 \\
64 & [268.5&396.5) & 8192 & 1 & 1 & 15 & 20 & 23 & 25 \\
32 & [396.5&460.5) & 2048 & 1 & 1 & 3 & 9 & 12 & 14 \\
32 & [460.5&588.5) & 4096 & 1 & 1 & 7 & 16 & 18 & 21 \\
32 & [588.5&844.5) & 8192 & 1 & 1 & 8 & 26 & 30 & 33 \\
32 & [844.5&1100.5) & 8192 & 1 & 1 & 1 & 12 & 20 & 23 \\
\tableline
\end{tabular}
\end{center}
\end{table*}
We use this template bank and decomposition for the remainder of this section.

@@

In this section we check the effect of the \SVD\ tolerance parameter defined
in \citet{Cannon:2010p10398}.  By changing the tolerance of the reconstruction
of the physical waveforms one directly affects the mismatch that results from
the truncation of the orthogonal filter matrix.  The conditions presented here
are more complicated than in the original work~\citep{Cannon:2010p10398} due to
the inclusion of the time-sliced templates and re-sampling.  Figure~%
\ref{fig:hist-svd-tolerance} demonstrates that it is possible to achieve
typical \SNR\ losses of $\ll1\%$.  However, we do notice that the mismatch
saturates with respect to the tolerance.  This could be the effect of the
re-sampling, or another \SNR\ loss that we did not model or expect.  However the
saturation is still an order of magnitude below our target mismatch of
$\sim$0.003.  We find that an \SVD\ tolerance of $\left(1-10^{-4}\right)$ is
adequate to achieve our target \SNR{} loss.

@@

\begin{figure*}[b]
	\subfloat[Mismatch versus \textsc{svd} tolerance]{\label{fig:hist-svd-tolerance}\includegraphics{figures/bw.pdf}}
	\subfloat[Mismatch versus $N^\shortuparrow$]{\label{fig:hist-interpolate}\includegraphics{figures/bw_resample.pdf}}
	\caption{Box-and-whisker plot of mismatch between nominal
template bank and \lloid\ measured impulse responses.  The upper and lower boundaries of
the boxes show the upper and lower quartiles; the lines in the center denote the medians.
The whiskers represent the minimum and maximum mismatch over all templates.  In 
\subref{fig:hist-svd-tolerance} the interpolation filter length is held fixed
at $N^\shortuparrow = 192$, while the \SVD\ tolerance is varied from
$\left(1-10^{-1}\right)$ to $\left(1-10^{-6}\right)$.  In \subref{fig:hist-interpolate}, the \SVD\ tolerance is fixed at $\left(1-10^{-6}\right)$ while $N^\shortuparrow$ is varied from 8 to 192 coefficients.}
\end{figure*}
